\bf Model Visualization Techniques for a Social Network Model

### 2017-04-13 paper.Rnw
add observed probabilities to histogram

The top row of Figure~\ref{makinggif} shows an edge being removed, and the bottom row shows one being added. In both cases

@@

<<histogramalters, fig.width = 8, fig.height=11, fig.cap="Probabilities of">>=
ansnullchains %>% group_by(period, rep) %>% 
  mutate(ms = row_number()) %>% 
  filter(ms == 1, period == 1) %>% 
  mutate(alterProb = exp(logAlterProb),
         ego = as.numeric(as.character(ego)),
         alter = as.numeric(as.character(alter))) %>% 
  ungroup() %>% 
  group_by(ego, alter) %>% 
  summarize(count = n(), alterProb = unique(alterProb)) %>% ungroup() %>% 
  group_by(ego) %>% 
  mutate(csum = cumsum(alterProb)) %>% 
  arrange(ego, csum) -> cumprobs 
cumprobs$ego <- factor(paste0("V",cumprobs$ego+1), levels = paste0("V", 1:16))

cumprobs %>% ggplot() + geom_histogram(aes(x = alter, weight = alterProb), color = 'black', fill = 'white', binwidth = 1) + scale_x_continuous(labels = paste0("V",1:16), breaks = 0:15) + coord_flip() + facet_wrap(~ego, labeller = "label_both") + theme_gray()

>>>>

The top row of Figure~\ref{makinggif} shows an edge being removed, and the bottom row shows one being added. In both cases, the nodes...

@@

<<histogramalters, fig.width = 8, fig.height=11, fig.cap="Probabilities of">>=
ansnullchains %>% group_by(period, rep) %>% 
  mutate(ms = row_number()) %>% 
  filter(ms == 1, period == 1) %>% 
  mutate(alterProb = exp(logAlterProb),
         ego = as.numeric(as.character(ego)),
         alter = as.numeric(as.character(alter))) %>% 
  ungroup() %>% 
  group_by(ego, alter) %>% 
  summarize(count = n(), alterProb = unique(alterProb)) %>% ungroup() %>% 
  group_by(ego) %>% 
  mutate(csum = cumsum(alterProb)) %>% 
  arrange(ego, csum) %>% 
  mutate(totego = sum(count), 
         empprob = count / totego) -> cumprobs 
cumprobs$ego <- factor(paste0("V",cumprobs$ego+1), levels = paste0("V", 1:16))

cumprobs %>% ggplot() + 
  geom_histogram(
    aes(x = alter, weight = alterProb), 
    color = 'black', fill = 'white', binwidth = 1) + 
  geom_point(aes(x = alter, y = empprob), color = 'red') + 
  scale_x_continuous(labels = paste0("V",1:16), breaks = 0:15) + coord_flip() + facet_wrap(~ego, labeller = "label_both") + theme_gray()
# 
# cumprobs %>% ggplot() + geom_histogram(aes(x = alter, weight = count), color = 'black', fill = 'white', binwidth = 1) + scale_x_continuous(labels = paste0("V",1:16), breaks = 0:15) + coord_flip() + facet_wrap(~ego, labeller = "label_both") + theme_gray()
